Incentivizing Exploration by Heterogeneous Users

### 2018-02-15 lower_bound.tex
addressed some comments
finished pass through payment proof

Under these advantages, myopic play is clearly optimal, so it suffices
to bound the regret of the myopic algorithm which never incentivizes
agents. \dkcomment{This feels ``clear'', but is it?}

@@

\dkcomment{Where did the 4 come from? Where did it go? Also, why did
  you have $\pi^3$ (instead of $\pi^2$) before? (I changed it.)}
\begin{align*}
\ExpectC{\Regret{t}}{\Noise{1} > 0, \Noise{2} > 0}
 & \geq \dkedit{4??} \cdot \frac{1}{8}
    \int_{0}^{\infty} \int_{0}^{\infty}
    \left( \frac{\Noise{1}}{1+\Noise{2}} \right)^2 \cdot
    \frac{\e^{-\frac{t \Noise{1}^2}{2}} \sqrt{t}}{\sqrt{2\pi}} \dd\Noise{1}
    \frac{\e^{-\frac{t \Noise{2}^2}{2}} \sqrt{t}}{\sqrt{2\pi}} \dd\Noise{2} \\
 & = \frac{1}{16\pi} \int_{0}^{\infty} \int_{0}^{\infty}
   \left( \frac{\Noise{1}}{\sqrt{t}+\Noise{2}} \right)^2
   \e^{-\Noise{1}^2/2} \e^{-\Noise{2}^2/2} \dd \Noise{1} \dd \Noise{2}.
\end{align*}

@@

\begin{align*}
\lim_{t \to \infty} \frac{\ExpectC{\Regret{t}}{\Noise{1} > 0, \Noise{2} > 0}}{\frac{1}{t}}
  & \geq
    \lim_{t \to \infty} \left( \frac{1}{16\pi} \cdot
    \int_{0}^{\infty} \int_{0}^{\infty}
    t \cdot \left( \frac{\Noise{1}}{\sqrt{t}+\Noise{2}} \right)^2
    \e^{-\Noise{1}^2/2} \e^{-\Noise{2}^2/2} \dd \Noise{1} \dd \Noise{2} \right) \\
  & = \frac{1}{16\pi} \cdot \int_{0}^{\infty} \int_{0}^{\infty}
    \lim_{t \to \infty}
    \left( t \cdot \left( \frac{\Noise{1}}{\sqrt{t}+\Noise{2}} \right)^2 \right)
    \e^{-\Noise{1}^2/2} \e^{-\Noise{2}^2/2} \dd \Noise{1} \dd \Noise{2} \\
  & = \frac{1}{16\pi} \cdot \int_{0}^{\infty} \int_{0}^{\infty}
    \e^{-\Noise{1}^2/2} \e^{-\Noise{2}^2/2} \dd \Noise{1} \dd \Noise{2}
  \; = \; \frac{1}{16 \pi}; 
\end{align*}

the second line is due to the monotone convergence theorem,
which can be applied because
$t \left(\frac{\Noise{1}}{\sqrt{t}+\Noise{2}}\right)^2$
is strictly increasing in $t$.
Because the expected regret in each time step is at least
$\Omega(1/t)$, the total expected regret is at least
$\Omega(\sum_{t=1}^{T}\frac{1}{t} = \Omega(\log(T))$.

>>>>

Under these advantages, myopic play is clearly optimal, so it suffices
to bound the regret of the myopic algorithm which never incentivizes
agents.

@@

\begin{align*}
\ExpectC{\Regret{t}}{\Noise{1} > 0, \Noise{2} > 0}
 & \geq \frac{1}{\Prob{\Noise{1}>0,\Noise{2}>0}} \cdot \frac{1}{8}
    \int_{0}^{\infty} \int_{0}^{\infty}
    \left( \frac{\Noise{1}}{1+\Noise{2}} \right)^2 \cdot
    \frac{\e^{-\frac{t \Noise{1}^2}{2}} \sqrt{t}}{\sqrt{2\pi}} \dd\Noise{1}
    \frac{\e^{-\frac{t \Noise{2}^2}{2}} \sqrt{t}}{\sqrt{2\pi}} \dd\Noise{2} \\
 & = \frac{1}{4\pi} \int_{0}^{\infty} \int_{0}^{\infty}
   \left( \frac{\Noise{1}}{\sqrt{t}+\Noise{2}} \right)^2
   \e^{-\Noise{1}^2/2} \e^{-\Noise{2}^2/2} \dd \Noise{1} \dd \Noise{2}.
\end{align*}

@@

\begin{align*}
\lim_{t \to \infty} \frac{\ExpectC{\Regret{t}}{\Noise{1} > 0, \Noise{2} > 0}}{\frac{1}{t}}
  & \geq
    \lim_{t \to \infty} \left( \frac{1}{4\pi} \cdot
    \int_{0}^{\infty} \int_{0}^{\infty}
    t \cdot \left( \frac{\Noise{1}}{\sqrt{t}+\Noise{2}} \right)^2
    \e^{-\Noise{1}^2/2} \e^{-\Noise{2}^2/2} \dd \Noise{1} \dd \Noise{2} \right) \\
  & = \frac{1}{4\pi} \cdot \int_{0}^{\infty} \int_{0}^{\infty}
    \lim_{t \to \infty}
    \left( t \cdot \left( \frac{\Noise{1}}{\sqrt{t}+\Noise{2}} \right)^2 \right)
    \e^{-\Noise{1}^2/2} \e^{-\Noise{2}^2/2} \dd \Noise{1} \dd \Noise{2} \\
  & = \frac{1}{4\pi} \cdot \int_{0}^{\infty} \int_{0}^{\infty}
    \e^{-\Noise{1}^2/2} \e^{-\Noise{2}^2/2} \dd \Noise{1} \dd \Noise{2}
  \; = \; \frac{1}{4 \pi}; 
\end{align*}

the second line is due to the monotone convergence theorem,
which can be applied because
$t \left(\frac{\Noise{1}}{\sqrt{t}+\Noise{2}}\right)^2$
is strictly increasing in $t$.
Because the expected regret in each time step is at least
$\Omega(1/t)$, the total expected regret is at least
$\Omega(\sum_{t=1}^{T}\frac{1}{t}) = \Omega(\log(T))$.

### 2018-02-15 payment-proof.tex
finished pass through payment proof

To reason about such estimation errors formally, we define
\emph{envelopes} of sample paths.
A sample path \SP captures all the random events affecting the
algorithm, i.e., the random draws \AgentV{t} of agents and the
noise \Noise[t] in the draws the pulled arms,
with an infite \dkcomment{Is it infinite?} time horizon.
\dkcomment{We should be consistent about using filtration vs.~sample
  path.}
\pfcomment{I removed discussion of filtrations and replaced them by discussion of history.}

@@

\begin{align*}
\hat{L}_\ell(t)
  & = \Set{\SP}{|\Err{t}{i}{j}(\SP)| \leq g(s(t,\SP),\ell)
    \mbox{ for all } i,j},\\
\Env[t]{1} & = \hat{L}_1(t)\\ 
\Env[t]{\ell} & = \hat{L}_{\ell} (t) - \hat{L}_{\ell-1} (t)
  \qquad \mbox{ for } \ell \geq 2.
\end{align*}

% \begin{align*}
% L'[\ell](t)
%   & = \Set{\SP}{|\Err{t}{i}{j}(\SP)|\leq g(s(t,\SP),\ell), \forall i,j\}
% \end{align*}
We call \Env[t]{\ell} the \Kth{\ell} envelope at time $t$.
\pfcomment{I believe we need the following definition for envelope $\ell$: 
$\hat{L}_\ell
  = \Set{\SP}{|\Err{t}{i}{j}(\SP)| \leq g(s(t,\SP),\ell)
    \mbox{ for all } i,j,t}$
This is what we use below in the proof of Theorem 3, plus a corresponding $L_\ell$.
It's ok to have $\hat{L}(t)$ defined as well, but if we are going to define the version without $t$ then maybe we don't need the one wiht $t$.
}

In words, \Env[t]{\ell} consists of all sample paths such that at time
$t$, all coordinates of all arm estimation errors are bounded by
$g(s, \ell)$, but at least one coordinate of one arm estimation error
is \emph{not} bounded by $g(s, \ell-1)$.
When $t$ is clear from the context, we omit it from the notation;
similarly, when \SP is clear, we omit it in the notation for
\Err{t}{i}{j}, payments, etc.
The importance of envelopes is that for small $\ell$, the payments are
tightly bounded, while for large $\ell$, the cumulative probability of
the sample paths in \Env[t]{\ell} is small.
This is captured by the following two lemmas.

\begin{lemma} \label{lem:sample-path-payment}
If $\SP \in \Env[t]{\ell}$ and $s(t,\SP) = s$, then
the payment in step $t$ is upper-bounded by
$\bar{c} (s,\ell) = \MAXR + 2 \Diam d \cdot g(s,\ell)$.
\dkcomment{Verify that the way I talk about $t$ vs.~$s$ is right.}
\end{lemma}

@@

\begin{lemma} \label{lem:envelope-probability}
For every $\ell \geq 2$ and $t$, we have that
$\Prob{\SP \in \Env[t]{\ell}} \leq 24 \ARMNUM d\exp(-1.8(\ell-1)^2)$. 
\end{lemma}

\begin{proof}
The proof idea is quite similar to the proof of
Lemma~\ref{lem:round-prob};
however, the specific form of the envelopes necessitates some subtle
changes in the specific forms of the bounds used.
For \SP to be in \Env[t]{\ell}, by definition, at least one coordinate
of at least one arm's estimation error must exceed $g(s(t,\SP),\ell-1)$.
For now, fix an arm $i$ and coordinate $j$.
Recall that $\NumPull{t}{i}(\SP) \geq s(t,\SP)$ is the number of times
that arm $i$ has been pulled by time $t$ under \SP.
We can express a bound on large deviations in terms of
the scaled estimation error
$\frac{\NumPull{t}{i} \cdot \Err{t}{i}{j}}{2\sigma}$:
\begin{align*}
\Prob{|\Err{t}{i}{j}| \geq g(s(t,\SP), \ell-1)}
& = \Prob{\frac{\NumPull{t}{i} \cdot \Err{t}{i}{j}}{2\sigma}
          \geq \frac{6\NumPull{t}{i}(\ell-1)}{s(t,\SP)^{2/5}}}\\
& \leq \; \Prob{\frac{\NumPull{t}{i} \cdot \Err{t}{i}{j}}{2\sigma}
          \geq 6\NumPull{t}{i}^{3/5}(\ell-1)}. 
\end{align*}

@@

\begin{align*}
6 \NumPull{t}{i}^{3/5}(\ell-1)
& \geq 5 \NumPull{t}{i}^{3/5} + \NumPull{t}{i}^{3/5}(\ell-1)  \\
& \geq \sqrt{0.6 \NumPull{t}{i} \log(\log_{1.1}(\NumPull{t}{i})+1)}
     + \sqrt{(\ell-1)^2 \NumPull{t}{i}}  \\
& \geq \sqrt{0.6\NumPull{t}{i}\log(\log_{1.1}(\NumPull{t}{i})+1)+(\ell-1)^2 \NumPull{t}{i}}. 
\end{align*}

Because the scaled estimation error
$\frac{\NumPull{t}{i} \cdot \Err{t}{i}{j}}{2\sigma}$
is a summation of $1/2$-Gaussian random variables, 
we can now apply Lemma~\ref{lem:ACI-inequality}
with $b(n) = (\ell-1)^2$ \dkcomment{omit dependence on $n$ here?},
to obtain that
\begin{align*}
\Prob{|\Err{t}{i}{j}| \geq g(s(t,\SP), \ell-1)}
& \leq 24 \e^{-1.8(\ell-1)^2}.
\end{align*}
Now, taking a union bound over all arms $i$ and
coordinates $j$ completes the proof.

@@

\begin{extraproof}{Theorem~\ref{rst:budget}}

\noindent\textbf{Step 3: Rewrite the total payment expression}.

\pfcomment{I deleted Step 2 and replaced it by this simpler argument}
Let $C(s)$ be the cost incurred in phase $s$.
In each phase, we can make at most $N$ payments, because each arm is incentivized at most once.
Noting that each sample path $\omega$ is in exactly one envelope and and using Lemma~\ref{lem:sample-path-payment}, we get
this bound on the cumulative payment:
\begin{align*}
\sum_{t=1}^{\infty}c(t) =\sum_{s=1}^{\infty}C(s)
\leq  \sum_{s=1}^{\infty}\sum_{\ell=1}^{\infty}\mathbbm{1}\{\SP\in \Env{\ell}\} N \bar{c}(s,\ell). 
\end{align*}

Set $g(s,\ell)$ to be $\frac{12\sigma \ell}{s^{2/5}}$.
Since if $|\Arm{i}{j}-\ArmE{t}{i}{j}|\leq \lambda$ is true $\forall i$, $\forall j$, then we know for those $\AgV\in \{\AgV:\AgV\cdot \ArmV{\Best{\AgV}}-\AgV \cdot \ArmV{\Second{\AgV}}> 2\Diam d\lambda\}$, they will correctly identify their best arm. Thus, if $|\Arm{i}{j}-\ArmE{t}{i}{j}|\leq \frac{12\sigma l}{s^{2/5}} \leq \frac{p^{-1}(\frac{\MinProb}{2})}{2\Diam d}$ $\forall i$ and $\forall j$, then the probability that an unincentivized agent would pull arm $i$ is at least $\frac{p}{2}$. Further, if time $t$ is in a phase $s$ that satisfies $1/log(s)\leq \MinProb/2$, then our algorithm will not incentivize pulling any arms. Denote $a_0=\frac{24\Diam d\sigma}{p^{-1}(\frac{\MinProb}{2})}$. In order to have $\frac{12\sigma l}{s^{2/5}}\leq \frac{p^{-1}(\frac{\MinProb}{2})}{2\Diam d}$, it is sufficient to have $s\geq \lceil (a_{0} l)^\frac{5}{2} \rceil$. In order to have $1/\log(s)\leq \frac{\MinProb}{2}$, we need $s\geq \exp(\frac{2}{\MinProb})$. Denote $s_2=\exp(\frac{2}{\MinProb})$. Thus, we know we can only incur regret \pfcomment{this should be payment cost, right?} for sample paths \SP in the $\ell^{th}$ envelope in the first $\max\{s_2,\lceil (a_0 \ell)^\frac{5}{2} \rceil\}$ phases.

Thus,
\begin{align*}
\sum_{t=1}^{\infty}c(t)\leq\sum_{\ell=1}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^\frac{5}{2} \rceil\}}\bar{c}(s,\ell)\mathbbm{1}\{\SP\in \Env{\ell}\}N. 
\end{align*}

Therefore,

\begin{align*}
&E\left[\sum_{t=1}^{\infty}c(t)\right] \\
\leq &\sum_{\ell=1}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^\frac{5}{2} \rceil\}}\bar{c}(s,\SP)\Prob{\SP \in \Env{\ell}}N  \\
=&\sum_{\ell=1}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^\frac{5}{2} \rceil\}}\left[\MAXR+2\Diam d\frac{12\sigma \ell}{s^{2/5}}\right]\Prob{\SP\in \Env{\ell}}N  \\
\leq &\sum_{\ell=1}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^\frac{5}{2} \rceil\}}\left[\MAXR+24\Diam d\sigma l\right]\Prob{\SP\in \Env{\ell}}N. 
\end{align*}

\noindent\textbf{Step 5: Final Step}

Thus,
\begin{align*}
&E\left[\sum_{t=1}^{\infty}c(t)\right]  \\
\leq&\sum_{\ell=1}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \ell\right]\Prob{\SP\in \Env{\ell}}N  \\
\leq& \sum_{s=1}^{\max\{s_2,\lceil (a_0)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \right]\Prob{\SP\in L[1]}N +\sum_{l=2}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \ell\right]\Prob{\SP\in \Env{\ell}}N  \\
\leq& \sum_{s=1}^{\max\{s_2,\lceil (a_0)^{5/2} \rceil\}}\left[R+24\Diam d\sigma \right]N +\sum_{\ell=2}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \ell\right]24\ARMNUM d e^{-1.8(\ell-1)^2}N \\
\leq & \left[\MAXR+24\Diam d\sigma \right]\ARMNUM \max\{s_2,\lceil (a_0)^{5/2} \rceil\}+\sum_{\ell=2}^{\infty}24\ARMNUM^2 d[\MAXR+24\Diam d\ell\sigma]\max\{s_2,\lceil (a_0 \ell)^{5/2} \rceil\} e^{-1.8(\ell-1)^2}  \\
=& O\left(\max\left\{\frac{\ARMNUM^2}{\MinProb^{5/2}},\ARMNUM^2\exp\left(\frac{2}{\MinProb}\right)\right\}\right). 
\end{align*}
\pfcomment{the above bound got tighter.  I didn't carry this forward anywhere where we report on / use the bound.}

\end{extraproof}

>>>>

To reason about such estimation errors formally, we define
\emph{envelopes} of sample paths.
A sample path \SP captures all the random events affecting the
algorithm, i.e., the random draws \AgentV{t} of agents and the
noise \NoiseV[t] in the draws the pulled arms,
with an infite \dkcomment{Is it infinite?} time horizon.
\dkcomment{We should be consistent about using filtration vs.~sample
  path.}
\pfcomment{I removed discussion of filtrations and replaced them by discussion of history.}

@@

\begin{align*}
\hat{L}_\ell
  & = \Set{\SP}{|\Err{t}{i}{j}(\SP)| \leq g(s(t,\SP),\ell)
    \mbox{ for all } i,j,t},\\
\Env{1} & = \hat{L}_1\\ 
\Env{\ell} & = \hat{L}_{\ell} - \hat{L}_{\ell-1}
  \qquad \mbox{ for } \ell \geq 2.
\end{align*}

% \begin{align*}
% L'[\ell](t)
%   & = \Set{\SP}{|\Err{t}{i}{j}(\SP)|\leq g(s(t,\SP),\ell), \forall i,j\}
% \end{align*}
We call \Env{\ell} the \Kth{\ell} envelope.
In words, \Env{\ell} consists of all sample paths such that at all times
$t$, all coordinates of all arm estimation errors are bounded by
$g(s, \ell)$,
but for at least one time $t$, at least one coordinate of one arm
estimation error is \emph{not} bounded by $g(s, \ell-1)$.
When \SP is clear, we omit it in the notation for
\Err{t}{i}{j}, payments, etc.
The importance of envelopes is that for small $\ell$, the payments are
tightly bounded, while for large $\ell$, the cumulative probability of
the sample paths in \Env{\ell} is small.
This is captured by the following two lemmas.

\begin{lemma} \label{lem:sample-path-payment}
If $\SP \in \Env{\ell}$ and $s(t,\SP) = s$, then
the payment in step $t$ is upper-bounded by
$\bar{c} (s,\ell) = \MAXR + 2 \Diam d \cdot g(s,\ell)$.
\dkcomment{Verify that the way I talk about $t$ vs.~$s$ is right.}
\end{lemma}

@@

\begin{lemma} \label{lem:envelope-probability}
For every $\ell \geq 2$, we have that
$\Prob{\SP \in \Env{\ell}} \leq 24 \ARMNUM d\exp(-1.8(\ell-1)^2)$. 
\end{lemma}

\begin{proof}
The proof idea is quite similar to the proof of
Lemma~\ref{lem:round-prob};
however, the specific form of the envelopes necessitates some subtle
changes in the specific forms of the bounds used.
For \SP to be in \Env{\ell}, by definition,
for at least one time $t$,
at least one coordinate of at least one arm's estimation error must
exceed $g(s(t,\SP),\ell-1)$.
For now, fix an arm $i$ and coordinate $j$.

Recall that $\NumPull{t}{i}(\SP) \geq s(t,\SP)$ is the number of times
that arm $i$ has been pulled by time $t$ under \SP.
We define the scaled estimation error
$S_{i,j}(t) := \frac{\NumPull{t}{i} \cdot \Err{t}{i}{j}}{2\sigma}$.
The advantage of $S_{i,j}(t)$ is that it is 
a summation of $1/2$-Gaussian random variables, 
so we will be able to apply Lemma~\ref{lem:ACI-inequality}.
First notice that we can express the desired probability as follows:

\begin{align*}
\Prob{|\Err{t}{i}{j}| \geq g(s(t,\SP), \ell-1)}
& = \Prob{S_{i,j}(t) \geq \frac{6\NumPull{t}{i}(\ell-1)}{s(t,\SP)^{2/5}}}\\
& \leq \; \Prob{S_{i,j}(t) \geq 6\NumPull{t}{i}^{3/5}(\ell-1)}. 
\end{align*}

@@

\begin{align*}
6 \NumPull{t}{i}^{3/5}(\ell-1)
& \geq 5 \NumPull{t}{i}^{3/5} + \NumPull{t}{i}^{3/5}(\ell-1)  \\
& \geq \sqrt{0.6 \NumPull{t}{i} \log(\log_{1.1}(\NumPull{t}{i})+1)}
     + \sqrt{(\ell-1)^2 \NumPull{t}{i}}  \\
& \geq \sqrt{0.6\NumPull{t}{i}\log(\log_{1.1}(\NumPull{t}{i})+1)+(\ell-1)^2 \NumPull{t}{i}}
\; =: \; h(\NumPull{t}{i}).
\end{align*}

Let the random stopping time $\tau_{i,j}$ be the first value of
\NumPull{t}{i} (i.e., the first pull of arm $i$) such that 
$S_{i,j}(\tau_{i,j}) > h(\NumPull{t}{i})$.
$\tau_{i,j} = \infty$ means that the estimation error never exceeds 
$h(\NumPull{t}{i})$.
We apply Lemma~\ref{lem:ACI-inequality}
to $S_{i,j}(t)$, with a stopping time of $\tau_{i,j}$ and
with $b(n) = (\ell-1)^2$ \dkcomment{omit dependence on $n$ here?}.
We obtain that the probability that $\tau_{i,j} < \infty$ and 
$S_{i,j}(\tau_{i,j}) > h(\tau_{i,j})$ is at most
$12 \e^{-1.8 b(n)}$.
By definition of $\tau_{i,j}$, the event is the same as simply
$\tau_{i,j} < \infty$.
Applying the lemma again to $-S_{i,j}(\tau_{i,j})$,
and taking a union bound over both cases,
gives us that the probability that there is \emph{any} time $t$ with
$|S_{i,j}(\NumPull{t}{i})| > h (\NumPull{t}{i})$
is at most $24 \e^{-1.8 b(n)}$.
Hence, the probability that the error at \emph{any} time $t$ exceeds
$g(s(t,\SP), \ell-1)$ is bounded by 
\begin{align*}
\Prob{|\Err{t}{i}{j}| \geq g(s(t,\SP), \ell-1)}
& \leq 24 \e^{-1.8(\ell-1)^2}.
\end{align*}
Now, taking a union bound over all arms $i$ and
coordinates $j$ completes the proof.

@@

Next, we show that for any sample path \SP in the envelope \Env{\ell},
we can bound the total number of payments made in terms of $\ell$.
Define $h(\ell) := \max \left( \exp(\frac{2}{\MinProb}),
\left( \frac{48 \sigma \ell \TieDensity \Diam d}{\MinProb} \right)^{5/2}
\right)$.

\begin{lemma} \label{lem:envelope-payments}
Let \SP be a sample path in \Env{\ell}.
Then, under \SP, the algorithm makes payments at most for the first 
$h(\ell)$ phases. 
\end{lemma}

\begin{proof}
The proof is similar to that of Lemma~\ref{lem:numP}.
Fix a sample path $\SP \in \Env{\ell}$.
Consider a phase $s > h(\ell)$.

By definition of \Env{\ell}, the coordinate-wise estimation errors at
times $t$ in phase $s$ are
$|\Arm{i}{j} - \ArmE{t}{i}{j}| \leq g(s,\ell)$.
In particular, all agent typs \AgV whose preference for their best arm
is sufficiently clear
($\AgV \cdot \ArmV{\Best{\AgV}} - \AgV \cdot \ArmV{\Second{\AgV}}
> 2\Diam d g(s,\ell)$) will pull their best arm.

By Lemma~\ref{lem:sdelta}, the \emph{total} measure of agents (across
all arms) whose best and second-best arm differ in utility by at most
$2\Diam d \cdot g(s,\ell)$ is at most $2L \Diam d \cdot g(s,\ell)$.
Substituting the definition of $g$, because 
$s > h(\ell) \geq \left( \frac{48 \sigma \ell \TieDensity \Diam d}{\MinProb} \right)^{5/2}$,
the total measure of these agents is bounded by $\MinProb/2$.

By Assumption~\ref{A3}, at least a \MinProb fraction of agents have
$i$ as their best arm, so even with estimation errors, at least
$\MinProb - \MinProb/2 = \MinProb/2$ fraction will still prefer to
pull arm $i$.

Because $s > h(\ell) \geq \exp(\frac{2}{\MinProb})$, 
we get that $1/\log(s) \leq \MinProb/2$, so in phase $s$,
the algorithm will not incentivize any arms whose pulling probability
is more than $\MinProb/2$, which is all arms.
So no payments will be made in phase $s$.
\end{proof}

\begin{extraproof}{Theorem~\ref{rst:budget}}
We can write the total expected payment as
\begin{align*}
  \Expect{\sum_{t=1}^{\infty} \PayA{t}}
& = \sum_{\ell = 1}^{\infty} \sum_{\SP \in \Env{\ell}}
  \Prob{\SP} \cdot \sum_{t=1}^{\infty} \PayA{t}(\SP)
\; = \; \sum_{\ell = 1}^{\infty} \sum_{\SP \in \Env{\ell}}
  \Prob{\SP} \cdot \sum_{s=1}^{\infty} \sum_{t: s(t,\SP) = s} \PayA{t}(\SP).
\end{align*}

By Lemma~\ref{lem:envelope-payments},
the payments are 0 for $s > h(\ell)$,
and by Lemma~\ref{lem:sample-path-payment},
when $\SP \in \Env{\ell}$ and $s(t,\SP) = s$, we can bound
$\PayA{t}(\SP) \leq \MAXR + 2 \Diam d \cdot g(s,\ell)$.
Furthermore, in any one phase, because each arm is incentivized at
most once, there are at most \ARMNUM payments total.
Substituting these bounds, we obtain that

\begin{align*}
  \Expect{\sum_{t=1}^{\infty} \PayA{t}}
& \leq \sum_{\ell = 1}^{\infty} \sum_{\SP \in \Env{\ell}} \Prob{\SP} \cdot
  \sum_{s=1}^{h(\ell)} \ARMNUM \cdot (\MAXR + 2 \Diam d \cdot g(s,\ell))
\\ & = \ARMNUM \cdot
  \sum_{\ell = 1}^{\infty} \Prob{\SP \in \Env{\ell}} \cdot
  \sum_{s=1}^{h(\ell)} \left( \MAXR + \frac{24 \Diam d \sigma \ell}{s^{2/5}} \right).
\end{align*}

We now lower-bound $s^{2/5} \geq 1$, split off the term for $\ell=1$
and bound $\Prob{\SP \in \Env{1}} \leq 1$, and apply
Lemma~\ref{lem:envelope-probability} to the remaining
$\Prob{\SP \in \Env{\ell}}$ terms, to bound

\begin{align*}
\Expect{\sum_{t=1}^{\infty} \PayA{t}}
& \leq
\ARMNUM \cdot \sum_{s=1}^{h(1)} (\MAXR + 24 \Diam d \sigma)
+ \ARMNUM \cdot
  \sum_{\ell = 2}^{\infty} 24 \ARMNUM d\exp(-1.8(\ell-1)^2) \cdot
  \sum_{s=1}^{h(\ell)} (\MAXR + 24 \Diam d \sigma \ell)
\\ & \leq
\ARMNUM \cdot h(1) \cdot (\MAXR + 24 \Diam d \sigma)
+ 24 \ARMNUM^2 d \cdot \sum_{\ell = 2}^{\infty}
     \exp(-1.8(\ell-1)^2) \cdot h(\ell) \cdot (\MAXR + 24 \Diam d \sigma \ell).
\end{align*}
Because $h(\ell)$ and $(\MAXR + 24 \Diam d \sigma \ell)$ grow
polynomially in $\ell$, whereas $\exp(-1.8(\ell-1)^2)$ decreases
exponentially in $\ell$, the sum is dominated by its first term, and
the overall expected payment is bounded by

\begin{align*}
O \left(\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma) \cdot h(1) \right)
& = 
O \left(\ARMNUM^2 \MAXR \Diam^2 \TieDensity d^3 \sigma
\cdot \exp(\frac{2}{\MinProb}) \right).
\end{align*}
\dkcomment{$p^{-5/2}$ is dominated by $\exp(2/p)$.}
\pfcomment{the bound got tighter.  I didn't carry this forward anywhere where we report on / use the bound.}
\end{extraproof}
